LMR with gam

### 2014-09-10 Rmd/lmfwithgam_bypft.Rmd
split gam analysis by pft or pftlong (Rmd)

source("load.R")
source("R/prepareDataset.R")

```{r eval=FALSE}
# Make quick pdf of gam by pftlong.
pdf("msowithpftandgam.pdf")
for(i in 1:nlevels(dat$pftlong)){
  d <- subset(dat, pftlong == levels(pftlong)[i])
  with(d, plot(lh.t, lmso, pch=19, col="dimgrey",main=levels(pftlong)[i]))
  gamplot("lh.t", "lmso", dfr=d, add=TRUE)

}
dev.off()

pdf("slawithpftandgam.pdf")
for(i in 1:nlevels(dat$pftlong)){
  d <- subset(dat, pftlong == levels(pftlong)[i])
  if(all(is.na(d$lsla)))next
  with(d, plot(lh.t, lsla, pch=19, col="dimgrey",main=levels(pftlong)[i]))
  gamplot("lh.t", "lsla", dfr=d, add=TRUE)

}
dev.off()

@@

### Leaf mass fraction and leaf area ratio by pft x biome

#### LMF
```{r lmf}
gamplotandpred(dataset2, "pftlong", "lmlf_mso")
```

### LAR
```{r lar}
gamplotandpred(dataset2, "pftlong", "lalf_mso")
```

@@

### Pipe model ratios by pft x biome

#### Leaf mass pipe ratio
```{r pipelmfpftlong}
pipelongmlf <- gamplotandpred(dataset2, "pftlong", "lmlf_astbh", Hs=c(3,10))
```

#### Leaf area pipe ratio
```{r pipeamfpftlong}
pipelongalf <- gamplotandpred(dataset2, "pftlong", "lalf_astbh", Hs=c(3,10))
```

@@

```{r}
slalong <- gamplotandpred(dataset2, "pftlong", "lsla", Hs=c(3,10))
```

### SLA and pipe model ratios across pft x biome

```{r}

long <- merge(slalong, pipelongmlf)
long$lma <- 1/long$lsla
long <- merge(long, pipelongalf)

makeci <- function(dfr, v){

  y <- dfr[,v]
  se <- dfr[,paste0(v,"_SE")]

  yl <- 10^(log10(y) - 2*se)
  yu <- 10^(log10(y) + 2*se)
return(data.frame(uci=yu, lci=yl))
}

addse <- function(dfr, x, y, direction, transformx=NULL){

  cix <- makeci(dfr,x)
  ciy <- makeci(dfr,y)
  if(!is.null(transformx)){
    cix <- transformx(cix)
    dfr[,x] <- transformx(dfr[,x])
  }

  arrows(x0=cix$lci, x1=cix$uci, y0=dfr[,y], y1=dfr[,y],
         code=3, angle=90, length=0.025)
  arrows(x0=dfr[,x], x1=dfr[,x], y0=ciy$lci, y1=ciy$uci,
         code=3, angle=90, length=0.025)

}

with(long,  plot(lma, lmlf_astbh, pch=19, col=c("grey","black")[as.factor(H)],
                 ylim=c(0,1000), xlim=c(0,0.4), 
                 panel.first={
                    addse(long, "lsla", "lmlf_astbh", transformx=function(x)1/x)
                  }))

with(long,  plot(lma, lalf_astbh, pch=19, col=c("grey","black")[as.factor(H)],
                 ylim=c(0,4500), xlim=c(0,0.4), 
                 panel.first={
                    addse(long, "lsla", "lalf_astbh", transformx=function(x)1/x)
                  }))

@@

```{r}

palette(rainbow(7))
with(dataset2, plot(log10(a.stbh), log10(a.lf), pch=19, col=pftlong))

# SLA problems!
pinus <- dataset2[grep("Pinus", dataset2$speciesMatched),]
pinus <- subset(pinus, !is.na(a.lf) & !is.na(m.lf))
with(pinus, tapply(a.lf/m.lf, Group, mean))

>>>>

source("load.R")
source("R/prepareDataset.R")
```

@@

@@

@@

```{r eval=FALSE}

dat <- subset(dataset2,!is.na(a.stbh) & !is.na(m.so))
datsp <- split(dat, dat$Group)
ii <- which(sapply(datsp,nrow) > 10)
lms <- lapply(datsp[ii],
              function(x)lm(log10(m.so) ~ log10(a.stbh), data=x))  
getr2 <- function(x)summary(x)$adj.r.squared

r2 <- sapply(lms, getr2)

@@

```{r eval=FALSE}
lme1 <- lme(log10(m.so) ~ log10(a.stbh), random=~log10(a.stbh)|Group, 
            data=dataset2, subset=pft=="EG", na.action=na.omit)
lme2 <- lme(log10(m.so) ~ log10(a.stbh), random=~log10(a.stbh)|Group, 
            data=dataset2, subset=pft=="EA", na.action=na.omit)
lme3 <- lme(log10(m.so) ~ log10(a.stbh), random=~log10(a.stbh)|Group, 
            data=dataset2, subset=pft=="DA", na.action=na.omit)

datsp <- split(dataset2, dataset2$Group)
R <- sapply(datsp, function(x)range(x$a.stbh))

makedf <- function(x){

  p <- coef(x)
  g <- rownames(p)
  r <- R[,g]
  df <- as.data.frame(cbind(p,t(r)))
  names(df) <- c("a","b","xmin","xmax")

  return(df)
}

p <- makedf(lme1)
pointsp <- function(x,...){
  for(i in 1:nrow(x)){
    ablinepiece(x$a[i], x$b[i], from=log10(x$xmin[i]), to=log10(x$xmax[i]), ...)
  }
}
with(dataset2, plot(log10(a.stbh), log10(m.so), type='n'))
pointsp(makedf(lme1), col="red")
pointsp(makedf(lme2), col="green3")
pointsp(makedf(lme3), col="blue")

### 2014-09-10 Rmd/lmfwithgam_bypftlong.Rmd
split gam analysis by pft or pftlong (Rmd)

source("load.R")
source("R/prepareDataset.R")

@@

### Leaf mass fraction and leaf area ratio by pft

#### LMF
```{r lmfpft}
gamplotandpred(dataset2, "pft", "lmlf_mso")
```

#### LAR
```{r larpft}
gamplotandpred(dataset2, "pft", "lalf_mso")
```

@@

### Pipe model ratios by pft

#### Leaf mass pipe ratio
```{r pipemlfpft}
pipemlf <- gamplotandpred(dataset2, "pft", "lmlf_astbh", Hs=c(3,10))
```

#### Leaf area pipe ratio
```{r pipealfpft}
pipealf <- gamplotandpred(dataset2, "pft", "lalf_astbh", Hs=c(3,10))
```

```{r}
sla <- gamplotandpred(dataset2, "pft", "lsla", Hs=c(3,10))
```

```{r}
slalong <- gamplotandpred(dataset2, "pftlong", "lsla", Hs=c(3,10))
```

@@

@@

>>>>

source("load.R")
source("R/prepareDataset.R")
```

@@

@@

#### SLA
```{r}
slalong <- gamplotandpred(dataset2, "pftlong", "lsla", Hs=c(3,10))
```

@@

```{r eval=FALSE}

@@

```{r eval=FALSE}
# Make sure no artefacts : any perfect R2 of m.so = f(a.stbh) ??
dat <- subset(dataset2,!is.na(a.stbh) & !is.na(m.so))
datsp <- split(dat, dat$Group)
ii <- which(sapply(datsp,nrow) > 10)
lms <- lapply(datsp[ii],
              function(x)lm(log10(m.so) ~ log10(a.stbh), data=x))  
getr2 <- function(x)summary(x)$adj.r.squared

r2 <- sapply(lms, getr2)

```{r}
lme1 <- lme(log10(m.so) ~ log10(a.stbh), random=~log10(a.stbh)|Group, 
            data=dataset2, subset=pft=="EG", na.action=na.omit)
lme2 <- lme(log10(m.so) ~ log10(a.stbh), random=~log10(a.stbh)|Group, 
            data=dataset2, subset=pft=="EA", na.action=na.omit)
lme3 <- lme(log10(m.so) ~ log10(a.stbh), random=~log10(a.stbh)|Group, 
            data=dataset2, subset=pft=="DA", na.action=na.omit)

datsp <- split(dataset2, dataset2$Group)
R <- sapply(datsp, function(x)range(x$a.stbh))

makedf <- function(x){

  p <- coef(x)
  g <- rownames(p)
  r <- R[,g]
  df <- as.data.frame(cbind(p,t(r)))
  names(df) <- c("a","b","xmin","xmax")

return(df)
}

p <- makedf(lme1)
pointsp <- function(x,...){
  for(i in 1:nrow(x)){
    ablinepiece(x$a[i], x$b[i], from=log10(x$xmin[i]), to=log10(x$xmax[i]), ...)
  }
}
with(dataset2, plot(log10(a.stbh), log10(m.so), type='n'))
pointsp(makedf(lme1), col="red")
pointsp(makedf(lme2), col="green3")
pointsp(makedf(lme3), col="blue")
